---
title: "UAM-AoI-Risk · Experiment BI"
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    css: styles.css
    navbar:
      - {title: "UAM-AoI-Risk", align: left}
runtime: shiny
---

```{r setup, include=FALSE}
# Source aggregator if present alongside dashboard
agg_script <- "aggregate_sim_data.R"
if (file.exists(agg_script)) source(agg_script, local=TRUE)

library(flexdashboard); library(shiny); library(dplyr); library(tidyr)
library(ggplot2); library(plotly); library(DT); library(readr)
library(purrr); library(stringr); library(forcats); library(scales)

POL_COLORS <- c(
  "round-robin"       = "#378ADD",
  "round-robin-aware" = "#6BAED6",
  "pf-classic"        = "#D85A30",
  "aoi-pure"          = "#1D9E75",
  "risk-aware"        = "#7F77DD",
  "max-weight"        = "#E6B22E",
  "max-weight-drift"  = "#F4A261",
  "lower_bound"       = "#BA7517"
)
POL_SHAPES <- c(
  "round-robin"       = 16,
  "round-robin-aware" = 1,
  "pf-classic"        = 17,
  "aoi-pure"          = 15,
  "risk-aware"        = 18,
  "max-weight"        = 8,
  "max-weight-drift"  = 11,
  "lower_bound"       = 4
)
POL_LINES <- c(
  "round-robin"       = "solid",
  "round-robin-aware" = "dotted",
  "pf-classic"        = "dashed",
  "aoi-pure"          = "solid",
  "risk-aware"        = "dotdash",
  "max-weight"        = "longdash",
  "max-weight-drift"  = "twodash",
  "lower_bound"       = "longdash"
)

theme_kadota <- function() {
  theme_minimal(base_family="mono",base_size=10) +
  theme(
    plot.background  = element_rect(fill="#161b22",colour=NA),
    panel.background = element_rect(fill="#0d1117",colour=NA),
    panel.grid.major = element_line(colour="#21262d",linewidth=0.35),
    panel.grid.minor = element_blank(),
    panel.border     = element_rect(colour="#30363d",fill=NA,linewidth=0.5),
    axis.text        = element_text(colour="#8b949e",size=8),
    axis.title       = element_text(colour="#c9d1d9",size=9,face="bold"),
    plot.title       = element_text(colour="#e6edf3",size=11,face="bold"),
    plot.subtitle    = element_text(colour="#8b949e",size=8),
    legend.background= element_rect(fill="#161b22",colour="#30363d",linewidth=0.4),
    legend.text      = element_text(colour="#c9d1d9",size=8),
    legend.title     = element_text(colour="#8b949e",size=7.5,face="bold"),
    legend.key       = element_rect(fill=NA,colour=NA),
    legend.key.width = unit(1.8,"lines"),
    strip.background = element_rect(fill="#21262d",colour=NA),
    strip.text       = element_text(colour="#c9d1d9",size=8.5,face="bold"),
    plot.margin      = margin(8,12,8,8)
  )
}

# ── Load all CSVs from a directory ──────────────────────────────────────────
load_dir <- function(dir_path) {
  # ── Fast path: pre-aggregated agg/ files (run aggregate_sim_data.py first)
  agg_dir <- file.path(dir_path, "agg")
  if (dir.exists(agg_dir) && file.exists(file.path(agg_dir,"agg_runs.csv"))) {
    message("[Dashboard] Loading pre-aggregated data from agg/ — fast mode")
    sr <- function(f) tryCatch(read_csv(f,show_col_types=FALSE), error=function(e) NULL)
    runs      <- sr(file.path(agg_dir,"agg_runs.csv"))
    drones    <- sr(file.path(agg_dir,"agg_drone.csv"))
    manifest  <- sr(file.path(agg_dir,"agg_manifest.csv"))
    risk_time <- sr(file.path(agg_dir,"agg_risk_time.csv"))
    cdf_data  <- sr(file.path(agg_dir,"agg_cdf.csv"))
    if (!is.null(runs) && nrow(runs)>0) {
      w_unc <- if("w_unc"%in%names(runs)) mean(as.numeric(runs$w_unc),na.rm=TRUE) else 0.33
      w_vid <- if("w_vid"%in%names(runs)) mean(as.numeric(runs$w_vid),na.rm=TRUE) else 0.34
      if (!"ewsaoi"%in%names(runs))
        runs <- runs %>% mutate(ewsaoi = w_unc*mean_h1 + w_vid*mean_h2)
      runs <- runs %>% mutate(
        c2_pct           = round(as.numeric(c2_share)*100, 1),
        frames_per_drone = as.numeric(total_frames)/pmax(as.integer(N),1),
        fdr_c2           = as.numeric(total_c2_ok)/
                           pmax(as.numeric(total_c2_ok)+as.numeric(total_c2_fail),1)
      )
    }
    return(list(runs=runs, drones=drones, series=risk_time,
                cdf=cdf_data, manifest=manifest, is_agg=TRUE))
  }

  # ── Slow path: raw CSVs (no agg/ found)
  message("[Dashboard] No agg/ found — loading raw CSVs. Run aggregate_sim_data.py to speed up.")
  empty <- list(runs=NULL,drones=NULL,series=NULL,cdf=NULL,manifest=NULL,is_agg=FALSE)
  if (is.null(dir_path)||!dir.exists(dir_path)) return(empty)
  files <- list.files(dir_path,pattern="\\.csv$",full.names=TRUE,recursive=TRUE)
  files <- files[!str_detect(basename(files),"^sweep_routing_summary")]
  if (!length(files)) return(empty)
  sr <- function(f) tryCatch(read_csv(f,show_col_types=FALSE),error=function(e) NULL)
  manifest   <- map_dfr(files[str_detect(files,"_manifest")], sr)
  drone_files <- files[str_detect(files,"_drone_summary")]
  drones <- bind_rows(compact(map(drone_files, function(f) {
    d <- sr(f); if(is.null(d)) return(NULL)
    run_id <- str_remove(basename(f),"_drone_summary\\.csv$")
    d$run_id <- run_id
    d$policy <- str_split(run_id,"_N")[[1]][1]
    d$N <- as.integer(str_extract(run_id,"(?<=_N)\\d+"))
    km <- str_extract(f,"(?<=/K)(\\d+)/")
    d$K <- if(!is.na(km)) as.integer(str_extract(km,"\\d+")) else 1L
    d
  })))
  if (is.null(drones)||nrow(drones)==0) return(empty)
  mp <- if(!is.null(manifest)&&"run_id"%in%names(manifest)) manifest else data.frame()
  w_unc_g <- if("w_unc"%in%names(mp)&&nrow(mp)>0) mean(as.numeric(mp$w_unc),na.rm=TRUE) else 0.33
  w_vid_g <- if("w_vid"%in%names(mp)&&nrow(mp)>0) mean(as.numeric(mp$w_vid),na.rm=TRUE) else 0.34
  runs <- drones %>%
    group_by(run_id,policy,N,K) %>%
    summarise(n_drones=n(), total_c2_ok=sum(slots_c2_ok), total_c2_fail=sum(slots_c2_fail),
              total_vid_ok=sum(slots_vid_ok), total_vid_fail=sum(slots_vid_fail),
              total_frames=sum(frames_delivered),
              mean_h1=mean(ifelse(mean_h1>0.01,mean_h1,
                (exit_slot-entry_slot)/pmax(slots_c2_ok,1)),na.rm=TRUE),
              mean_h2=mean(ifelse(mean_h2>0.01,mean_h2,
                (exit_slot-entry_slot)/pmax(frames_delivered,1)),na.rm=TRUE),
              mean_r_vid=mean(suppressWarnings(as.numeric(mean_r_vid)),na.rm=TRUE),
              mean_r_tot=mean(suppressWarnings(as.numeric(mean_r_tot)),na.rm=TRUE),
              .groups="drop") %>%
    mutate(ewsaoi=w_unc_g*mean_h1+w_vid_g*mean_h2,
           c2_share=total_c2_ok/pmax(total_c2_ok+total_vid_ok,1),
           c2_pct=round(c2_share*100,1),
           frames_per_drone=total_frames/pmax(n_drones,1))
  if("run_id"%in%names(mp)&&nrow(mp)>0) {
    keep <- intersect(c("run_id","L_vid","w_coh","corridor_length","update_rate",
                        "w_unc","w_map","w_vid","sim_slots","corridor_capacity"),names(mp))
    runs <- left_join(runs,mp[,keep],by="run_id")
  }
  # ── Join routing_mode / num_routes from sweep_routing_summary files ──────
  sw_dir <- file.path(dir_path,"sweep_routing")
  if (dir.exists(sw_dir)) {
    sw_files <- list.files(sw_dir, pattern="^sweep_routing_summary\\.csv$",
                           full.names=TRUE, recursive=TRUE)
    sw_files <- sw_files[!str_detect(sw_files,"sweep_routing_summary_all")]
    if (length(sw_files)>0) {
      sw_all <- bind_rows(compact(map(sw_files, function(f) {
        km  <- str_extract(f,"(?<=/K)(\\d+)/")
        d   <- sr(f); if(is.null(d)||nrow(d)==0) return(NULL)
        d$K <- if(!is.na(km)) as.integer(str_extract(km,"\\d+")) else NA_integer_
        d
      })))
      need <- c("K","num_drones","policy","routing_mode","num_routes")
      if (all(need%in%names(sw_all))) {
        sw_idx <- sw_all %>%
          rename(N=num_drones) %>%
          mutate(N=as.integer(N), K=as.integer(K)) %>%
          group_by(K,N,policy) %>%
          mutate(pos=row_number()) %>%
          ungroup() %>%
          select(K,N,policy,pos,routing_mode,num_routes)
        runs <- runs %>%
          mutate(ts_=str_extract(run_id,"\\d{8}_\\d{6}$")) %>%
          group_by(K,N,policy) %>%
          arrange(ts_,.by_group=TRUE) %>%
          mutate(pos=row_number()) %>%
          ungroup() %>%
          left_join(sw_idx,by=c("K","N","policy","pos")) %>%
          select(-ts_,-pos)
      }
    }
  }
  list(runs=runs,drones=drones,series=NULL,cdf=NULL,manifest=manifest,is_agg=FALSE)
}


# ── Lower bound (Kadota Algorithm 1 simplified) ────────────────────────────
compute_lb <- function(N, K=1, p_s=0.9, w_unc=0.33, w_vid=0.34) {
  # Kadota Theorem 2 lower bound on EWSAoI (not on h1 alone).
  # EWSAoI = w_unc*h1 + w_vid*h2 — this is what the LB bounds.
  # With 2N identical sources (C2 + video per drone), K=1, lambda=1:
  #   q_i = min(1, K/(2N)) * p_s   (scheduling fraction * success prob)
  #   LB_source = 1/q + 1           (per-source AoI contribution)
  #   LB = (1/(2N)) * [N*(w_unc*(1/q+1)) + N*(w_vid*(1/q+1))]
  #      = (w_unc + w_vid) * (1/q + 1)
  q  <- min(1, K / (2*N)) * p_s
  lb <- (w_unc + w_vid) * (1/max(q, 0.001) + 1)
  lb
}

# ── Plot helpers ────────────────────────────────────────────────────────────
dark_plotly <- function(p) {
  ggplotly(p, tooltip="text") %>%
    layout(paper_bgcolor="#161b22",plot_bgcolor="#0d1117",
           font=list(color="#c9d1d9",family="monospace",size=11),
           legend=list(bgcolor="#161b22",bordercolor="#30363d",borderwidth=1)) %>%
    config(displayModeBar=FALSE)
}
no_data <- function(msg="Load CSV data and click Reload") {
  plot_ly(x=0,y=0,type="scatter",mode="markers",marker=list(opacity=0),hoverinfo="none") %>%
    layout(title=list(text=msg,font=list(color="#484f58",size=13),x=0.5),
           paper_bgcolor="#161b22",plot_bgcolor="#0d1117",
           xaxis=list(visible=FALSE),yaxis=list(visible=FALSE),showlegend=FALSE) %>%
    config(displayModeBar=FALSE)
}
```

Sidebar {.sidebar data-width=230}
=====================================

```{r}
tags$h4("Data",style="color:#58a6ff;font-size:13px;margin:0 0 8px 0")
textInput("csv_dir",NULL,value="csv_export",placeholder="path/to/csv_export/")
actionButton("reload","Reload",
  style="width:100%;background:#21262d;color:#58a6ff;border:1px solid #30363d;font-size:11px;padding:5px;border-radius:4px;margin-bottom:10px")
tags$hr(style="border-color:#21262d;margin:6px 0")
tags$h4("Filters",style="color:#58a6ff;font-size:13px;margin:0 0 8px 0")
uiOutput("ui_pol"); uiOutput("ui_N"); uiOutput("ui_capacity")
uiOutput("ui_K"); uiOutput("ui_Lvid")
uiOutput("ui_routing_mode"); uiOutput("ui_num_routes")
tags$hr(style="border-color:#21262d;margin:6px 0")
tags$h4("Axes",style="color:#58a6ff;font-size:13px;margin:0 0 8px 0")
selectInput("xvar","X axis",
  choices=c("N drones"="N","Capacity (relay)"="corridor_capacity",
            "L_vid"="L_vid","corridor_km"="corridor_km"),selected="N")
selectInput("yvar","Y axis",
  choices=c("EWSAoI (weighted sum)"="ewsaoi",
            "C2 AoI h1 (component)"="mean_h1",
            "Video AoI h2 (component)"="mean_h2",
            "C2 share %"="c2_pct","Frames/drone"="frames_per_drone",
            "FDR C2"="fdr_c2"),selected="ewsaoi")
checkboxInput("show_lb","Show lower bound",TRUE)
checkboxInput("log_y","Log Y",FALSE)
tags$hr(style="border-color:#21262d;margin:6px 0")
tags$hr(style="border-color:#21262d;margin:6px 0")
tags$p("Pre-process",style="color:#58a6ff;font-size:11px;font-weight:500;margin:0 0 5px 0")
actionButton("run_agg","⚙ Aggregate CSVs",
  style="width:100%;background:#162521;color:#3fb950;border:1px solid #1a4731;
         font-size:11px;padding:4px;border-radius:4px;margin-bottom:3px")
verbatimTextOutput("agg_log",placeholder=TRUE)
tags$p("Run once per sweep for fast loading.",
  style="color:#484f58;font-size:9px;margin:2px 0;font-family:monospace")
tags$hr(style="border-color:#21262d;margin:6px 0")
tags$p("UAM-AoI-Risk · INFOCOM",style="color:#484f58;font-size:9px;margin:0;font-family:monospace")
```

```{r, context="server"}
# ── Run filter helper — handles '(all runs)' sentinel ────────────────────
filter_run <- function(d, sel_run) {
  if (is.null(d)||nrow(d)==0) return(d)
  if (is.null(sel_run)||isTRUE(sel_run=="__all__")||!"run_id"%in%names(d)) return(d)
  d %>% filter(run_id==sel_run)
}

# ── Aggregate button ─────────────────────────────────────────────────────
agg_log_rv <- reactiveVal("")
observeEvent(input$run_agg, {
  dir <- isolate(input$csv_dir)
  if (!dir.exists(dir)) { agg_log_rv("Directory not found."); return() }
  if (!exists("aggregate_sim_data")) {
    agg_log_rv("aggregate_sim_data.R not found.\nPlace it beside uam_dashboard.Rmd."); return()
  }
  agg_log_rv("Running...")
  tryCatch({
    res <- aggregate_sim_data(dir, verbose=FALSE)
    agg_log_rv(sprintf("Done! %d runs.\nClick Reload.", nrow(res$runs)))
  }, error=function(e) agg_log_rv(paste("Error:", conditionMessage(e))))
})
output$agg_log <- renderText(agg_log_rv())

dat <- eventReactive(input$reload, { load_dir(input$csv_dir) },
  ignoreNULL=FALSE, ignoreInit=FALSE)

runs_r <- reactive({
  d <- dat()$runs
  if (is.null(d)||nrow(d)==0||!"policy"%in%names(d)) return(NULL)
  d <- d %>% mutate(c2_pct = c2_share*100)
  if (!is.null(input$sel_pol) && length(input$sel_pol)>0)
    d <- d %>% filter(policy %in% input$sel_pol)
  if (!is.null(input$sel_N) && input$sel_N!="all")
    d <- d %>% filter(N==as.integer(input$sel_N))
  if (!is.null(input$sel_Lvid) && input$sel_Lvid!="all" && "L_vid"%in%names(d))
    d <- d %>% filter(L_vid==as.integer(input$sel_Lvid))
  if (!is.null(input$sel_K) && input$sel_K!="all" && "K"%in%names(d))
    d <- d %>% filter(K==as.integer(input$sel_K))
  if (!is.null(input$sel_capacity) && input$sel_capacity!="all" && "corridor_capacity"%in%names(d))
    d <- d %>% filter(corridor_capacity==as.integer(input$sel_capacity))
  if (!is.null(input$sel_routing_mode) && input$sel_routing_mode!="all" && "routing_mode"%in%names(d))
    d <- d %>% filter(routing_mode==input$sel_routing_mode)
  if (!is.null(input$sel_num_routes) && input$sel_num_routes!="all" && "num_routes"%in%names(d))
    d <- d %>% filter(num_routes==as.integer(input$sel_num_routes))
  if (nrow(d)==0) return(NULL)
  # Compute EWSAoI = w_unc*h1 + w_vid*h2 (the metric the LB actually bounds)
  w_unc <- if("w_unc"%in%names(d)) mean(d$w_unc,na.rm=TRUE) else 0.33
  w_vid <- if("w_vid"%in%names(d)) mean(d$w_vid,na.rm=TRUE) else 0.34
  d <- d %>% mutate(ewsaoi = w_unc*mean_h1 + w_vid*mean_h2)
  d
})

output$ui_pol <- renderUI({
  d <- dat()$runs; if(is.null(d)||!"policy"%in%names(d)) return(NULL)
  pols <- unique(d$policy)
  checkboxGroupInput("sel_pol","Policies",choices=pols,selected=pols)
})
output$ui_N <- renderUI({
  d <- dat()$runs; if(is.null(d)||!"N"%in%names(d)) return(NULL)
  ns <- sort(unique(d$N))
  selectInput("sel_N","N drones",choices=c("(all)"="all",ns),selected="all")
})
output$ui_Lvid <- renderUI({
  d <- dat()$runs
  if(is.null(d)||!"L_vid"%in%names(d)||all(is.na(d$L_vid))) return(NULL)
  vs <- sort(unique(na.omit(d$L_vid)))
  if(length(vs)<2) return(NULL)
  selectInput("sel_Lvid","L_vid",choices=c("(all)"="all",vs),selected="all")
})
output$ui_K <- renderUI({
  d <- dat()$runs
  if(is.null(d)||!"K"%in%names(d)) return(NULL)
  ks <- sort(unique(na.omit(d$K)))
  if(length(ks)<2) return(NULL)
  selectInput("sel_K","K slots",choices=c("(all)"="all",ks),selected="all")
})
load_r <- reactive({
  d <- runs_r()
  if (is.null(d) || nrow(d) == 0) return(NULL)
  w_unc_v <- if("w_unc"%in%names(d)) mean(as.numeric(d$w_unc), na.rm=TRUE) else 0.33
  w_vid_v  <- if("w_vid"%in%names(d)) mean(as.numeric(d$w_vid), na.rm=TRUE) else 0.34
  # Compute all derived columns before summarise to avoid "not found" errors.
  d %>%
    mutate(
      K_n      = as.numeric(K),
      N_n      = as.numeric(N),
      rho_     = N_n / pmax(K_n, 1),
      vid_fdr_ = as.numeric(total_vid_ok) /
                 pmax(as.numeric(total_vid_ok) + as.numeric(total_vid_fail), 1),
      fdr_c2_  = as.numeric(total_c2_ok) /
                 pmax(as.numeric(total_c2_ok) + as.numeric(total_c2_fail), 1),
      ss_n_    = suppressWarnings(as.numeric(sim_slots)),
      tput_c2_ = as.numeric(total_c2_ok) / pmax(ss_n_, 1),
      r_tot_n_ = suppressWarnings(as.numeric(mean_r_tot))
    ) %>%
    group_by(policy, rho_) %>%
    summarise(
      r_sys            = mean(r_tot_n_,        na.rm=TRUE),
      ewsaoi           = mean(ewsaoi,           na.rm=TRUE),
      mean_h1          = mean(mean_h1,           na.rm=TRUE),
      mean_h2          = mean(mean_h2,           na.rm=TRUE),
      frames_per_drone = mean(frames_per_drone,  na.rm=TRUE),
      vid_fdr          = mean(vid_fdr_,          na.rm=TRUE),
      tput_c2          = mean(tput_c2_,          na.rm=TRUE),
      fdr_c2           = mean(fdr_c2_,           na.rm=TRUE),
      N_rep            = mean(N_n),
      K_rep            = mean(K_n),
      .groups          = "drop"
    ) %>%
    rename(rho = rho_) %>%
    mutate(
      lb_aoi = mapply(function(n, k)
        compute_lb(max(round(n), 1L), K=max(round(k), 1L),
                   w_unc=w_unc_v, w_vid=w_vid_v),
        N_rep, K_rep)
    )
})

net_r <- reactive({
  d <- runs_r()
  if (is.null(d) || nrow(d) == 0) return(NULL)
  ur <- if ("update_rate" %in% names(d)) as.numeric(d$update_rate) else rep(7,  nrow(d))
  ss <- if ("sim_slots"   %in% names(d)) as.numeric(d$sim_slots)   else rep(NA, nrow(d))
  kk <- if ("K"           %in% names(d)) as.numeric(d$K)           else rep(1,  nrow(d))
  nd <- if ("n_drones"    %in% names(d)) as.numeric(d$n_drones)    else as.numeric(d$N)
  d %>% mutate(
    ur_ = ur, ss_ = ss, kk_ = kk, nd_ = nd,
    tput_c2_pkt_s = (total_c2_ok  / pmax(ss_, 1)) * ur_,
    tput_vid_fps  = (total_frames / pmax(ss_, 1)) * ur_ / pmax(nd_, 1),
    fdr_c2_n  = total_c2_ok  / pmax(total_c2_ok  + total_c2_fail,  1),
    fdr_vid_n = total_vid_ok / pmax(total_vid_ok + total_vid_fail, 1),
    loss_c2   = 1 - fdr_c2_n,
    loss_vid  = 1 - fdr_vid_n,
    chan_util  = (total_c2_ok + total_c2_fail + total_vid_ok + total_vid_fail) /
                 pmax(ss_ * kk_, 1),
    lat_c2_s  = mean_h1 / ur_,
    lat_vid_s = mean_h2 / ur_
  ) %>% select(-ur_, -ss_, -kk_, -nd_)
})

output$ui_capacity <- renderUI({
  d <- dat()$runs
  if(is.null(d)||!"corridor_capacity"%in%names(d)||all(is.na(d$corridor_capacity))) return(NULL)
  caps <- sort(unique(na.omit(as.integer(d$corridor_capacity))))
  caps <- caps[caps > 0]
  if(length(caps) < 2) return(NULL)
  selectInput("sel_capacity","Capacity",
    choices=c("(all)"="all", setNames(caps, paste(caps, "drones"))),
    selected="all")
})
output$ui_routing_mode <- renderUI({
  d <- dat()$runs
  if(is.null(d)||!"routing_mode"%in%names(d)||all(is.na(d$routing_mode))) return(NULL)
  modes <- sort(unique(na.omit(d$routing_mode)))
  if(length(modes)<2) return(NULL)
  selectInput("sel_routing_mode","Routing",
    choices=c("(all)"="all","Static"="static","Risk-A*"="risk_astar"),
    selected="all")
})
output$ui_num_routes <- renderUI({
  d <- dat()$runs
  if(is.null(d)||!"num_routes"%in%names(d)||all(is.na(d$num_routes))) return(NULL)
  nr <- sort(unique(na.omit(as.integer(d$num_routes))))
  if(length(nr)<2) return(NULL)
  selectInput("sel_num_routes","Routes",
    choices=c("(all)"="all",setNames(nr, paste(nr,"route(s)"))),
    selected="all")
})
```

Overview {data-icon="fa-chart-line"}
=====================================

Row {data-height=105}
-------------------------------------

### Runs
```{r}
renderValueBox({
  d <- dat()$runs; n<-if(is.null(d)||nrow(d)==0) 0 else nrow(d)
  valueBox(n,"Runs",icon="fa-database",color=if(n>0)"primary" else "warning")
})
```

### Policies
```{r}
renderValueBox({
  d <- dat()$runs
  n<-if(is.null(d)||nrow(d)==0||!"policy"%in%names(d)) 0 else length(unique(d$policy))
  valueBox(n,"Policies",icon="fa-code-branch",color="info")
})
```

### Best h1
```{r}
renderValueBox({
  d <- runs_r(); if(is.null(d)){valueBox("--","Best h1",color="warning");return()}
  b <- d %>% arrange(mean_h1) %>% slice(1)
  valueBox(sprintf("%.1f sl",b$mean_h1),paste0(b$policy," N=",b$N),icon="fa-trophy",color="success")
})
```

### Best h2
```{r}
renderValueBox({
  d <- runs_r(); if(is.null(d)){valueBox("--","Best h2",color="warning");return()}
  b <- d %>% arrange(mean_h2) %>% slice(1)
  valueBox(sprintf("%.1f sl",b$mean_h2),paste0(b$policy," N=",b$N),icon="fa-video",color="success")
})
```

### N values
```{r}
renderValueBox({
  d <- runs_r(); if(is.null(d)){valueBox("--","N values",color="warning");return()}
  ns <- sort(unique(d$N))
  valueBox(paste(ns,collapse=","),"N tested",icon="fa-helicopter",color="info")
})
```

Row {data-height=480}
-------------------------------------

### Main sweep chart {data-width=680}
```{r}
renderPlotly({
  d <- runs_r(); if(is.null(d)) return(no_data())
  xv <- input$xvar%||%"N"; yv <- input$yvar%||%"mean_h1"
  if(!xv%in%names(d)) xv<-"N"
  if(!yv%in%names(d)) yv<-"mean_h1"
  ylab <- switch(yv,
    ewsaoi="EWSAoI = w_unc·h1 + w_vid·h2 (slots)",
    mean_h1="C2 AoI h1 (slots) [component only]",
    mean_h2="Video AoI h2 (slots) [component only]",
    c2_pct="C2 slot share (%)",frames_per_drone="Frames/drone",fdr_c2="FDR C2",yv)
  xlab <- switch(xv,N="Number of drones N",L_vid="Update length L_vid",
                 corridor_km="Corridor length (km)",xv)
  
  d2 <- d %>% mutate(
    policy=factor(policy,levels=intersect(names(POL_COLORS),unique(policy))),
    xv=.data[[xv]], yv=.data[[yv]],
    tip=sprintf("<b>%s</b><br>%s=%g<br>%s=%.2f",policy,xlab,xv,ylab,yv))
  
  # Add lower bound — ONLY valid when Y axis = EWSAoI (weighted sum)
  # LB bounds EWSAoI = w_unc*h1 + w_vid*h2, not h1 or h2 individually.
  lb_data <- NULL
  if(isTRUE(input$show_lb) && yv=="ewsaoi" && "N"%in%names(d)) {
    w_unc_v <- if("w_unc"%in%names(d)) mean(d$w_unc,na.rm=TRUE) else 0.33
    w_vid_v  <- if("w_vid"%in%names(d)) mean(d$w_vid,na.rm=TRUE) else 0.34
    ns <- sort(unique(d$N))
    K_sel <- if(!is.null(input$sel_K)&&input$sel_K!="all") as.integer(input$sel_K) else
             if("K"%in%names(d)) as.integer(round(mean(d$K,na.rm=TRUE))) else 1L
    lb_vals <- sapply(ns, function(n) compute_lb(n, K=K_sel, w_unc=w_unc_v, w_vid=w_vid_v))
    xv_vals <- if(xv=="N") ns else rep(mean(d[[xv]],na.rm=TRUE),length(ns))
    lb_data <- tibble(xv=xv_vals, yv=lb_vals,
                      policy=factor("lower_bound",levels=names(POL_COLORS)),
                      tip=sprintf("<b>Lower Bound (EWSAoI)</b><br>N=%d<br>LB=%.2f",ns,lb_vals))
    d2 <- bind_rows(d2, lb_data)
  } else if(isTRUE(input$show_lb) && yv!="ewsaoi") {
    # Remind user: LB only shown for EWSAoI axis
    showNotification("Lower bound is only shown when Y axis = EWSAoI (weighted sum).
h1 and h2 individually can be below the LB — this is expected.", type="message", duration=5)
  }
  
  p <- ggplot(d2,aes(x=xv,y=yv,colour=policy,shape=policy,linetype=policy,text=tip)) +
    geom_line(linewidth=0.85,na.rm=TRUE) +
    geom_point(size=3,na.rm=TRUE) +
    scale_colour_manual(values=POL_COLORS,name="Policy",
      breaks=intersect(names(POL_COLORS),levels(d2$policy))) +
    scale_shape_manual(values=POL_SHAPES,name="Policy",
      breaks=intersect(names(POL_SHAPES),levels(d2$policy))) +
    scale_linetype_manual(values=POL_LINES,name="Policy",
      breaks=intersect(names(POL_LINES),levels(d2$policy))) +
    labs(x=xlab,y=ylab,title=paste(ylab,"vs",xlab),
         subtitle="All policies · lower = better") +
    theme_kadota()
  if(isTRUE(input$log_y)) p <- p + scale_y_log10(labels=label_comma())
  dark_plotly(p)
})
```

### Policy ranking {data-width=280}
```{r}
renderPlotly({
  d <- runs_r(); if(is.null(d)) return(no_data())
  yv <- input$yvar%||%"mean_h1"; if(!yv%in%names(d)) yv<-"mean_h1"
  rank_df <- d %>% group_by(policy) %>%
    summarise(val=mean(.data[[yv]],na.rm=TRUE),.groups="drop") %>%
    arrange(val) %>% mutate(policy=fct_reorder(policy,val),
      tip=sprintf("<b>%s</b><br>%.2f",policy,val),
      col=POL_COLORS[as.character(policy)])
  plot_ly(rank_df,x=~val,y=~policy,type="bar",orientation="h",
    text=~tip,hoverinfo="text",
    marker=list(color=rank_df$col,line=list(color="#30363d",width=0.5))) %>%
    layout(title=list(text="Ranking",font=list(color="#e6edf3",size=12)),
           xaxis=list(title=yv,gridcolor="#21262d",color="#8b949e"),
           yaxis=list(title="",gridcolor="#21262d",color="#c9d1d9"),
           paper_bgcolor="#161b22",plot_bgcolor="#0d1117",
           font=list(color="#c9d1d9",family="monospace"),showlegend=FALSE,
           margin=list(l=90,r=10,t=40,b=40)) %>%
    config(displayModeBar=FALSE)
})
```

AoI Figures {data-icon="fa-chart-line"}
=====================================

Row {.tabset data-height=510}
-------------------------------------

### h1 × h2 Safety-Coherence Region
```{r}
renderPlotly({
  d <- runs_r(); if(is.null(d)||!"mean_h2"%in%names(d)) return(no_data())
  d2 <- d %>% filter(!is.na(mean_h2)) %>%
    mutate(policy=factor(policy,levels=names(POL_COLORS)),
           tip=sprintf("<b>%s</b><br>N=%d<br>h1=%.1f<br>h2=%.1f",policy,N,mean_h1,mean_h2))
  p <- ggplot(d2,aes(x=mean_h1,y=mean_h2,colour=policy,shape=policy,text=tip)) +
    geom_point(size=3.5,alpha=0.9) +
    geom_path(aes(group=policy),linewidth=0.5,alpha=0.4,na.rm=TRUE) +
    scale_colour_manual(values=POL_COLORS,name="Policy") +
    scale_shape_manual(values=POL_SHAPES,name="Policy") +
    labs(x="C2 AoI h1 (slots)",y="Video AoI h2 (slots)",
         title="Safety-Coherence Region  S(W,rho)",
         subtitle="Pareto frontier h1 vs h2 — each point = one run") +
    theme_kadota()
  dark_plotly(p)
})
```

### EWSAoI vs N (scalability)
```{r}
renderPlotly({
  d <- runs_r(); if(is.null(d)) return(no_data())
  d2 <- d %>% mutate(policy=factor(policy,levels=names(POL_COLORS)),
    ewsaoi=if("ewsaoi"%in%names(d)) ewsaoi else NA,
    tip=sprintf("<b>%s</b><br>N=%d<br>EWSAoI=%.1f<br>h1=%.1f<br>h2=%.1f",
                policy,N,ifelse(is.na(ewsaoi),NA,ewsaoi),mean_h1,mean_h2))
  p <- ggplot(d2,aes(x=N,y=ifelse("ewsaoi"%in%names(d2),ewsaoi,mean_h1),
                     colour=policy,shape=policy,linetype=policy,text=tip)) +
    geom_line(linewidth=0.85,na.rm=TRUE) + geom_point(size=3,na.rm=TRUE) +
    scale_colour_manual(values=POL_COLORS,name="Policy") +
    scale_shape_manual(values=POL_SHAPES,name="Policy") +
    scale_linetype_manual(values=POL_LINES,name="Policy") +
    labs(x="Number of drones N",y="EWSAoI h1 (slots)",
         title="EWSAoI vs N  — scalability",
         subtitle="Scalability — fixed corridor, all policies") + theme_kadota()
  dark_plotly(p)
})
```

### Optimality ratio psi
```{r}
renderPlotly({
  d <- runs_r(); if(is.null(d)) return(no_data())
  ns <- sort(unique(d$N))
  lb <- tibble(N=ns, lb=sapply(ns,compute_lb))
  d2 <- d %>% left_join(lb,by="N") %>% filter(!is.na(lb),lb>0) %>%
    mutate(ewsaoi=if("ewsaoi"%in%names(.)) ewsaoi else 0.33*mean_h1+0.34*mean_h2,
           psi=ewsaoi/lb,
           policy=factor(policy,levels=names(POL_COLORS)),
           tip=sprintf("<b>%s</b><br>N=%d<br>psi=%.2f<br>EWSAoI=%.1f<br>LB=%.1f",
                       policy,N,psi,ewsaoi,lb))
  p <- ggplot(d2,aes(x=N,y=psi,colour=policy,shape=policy,linetype=policy,text=tip)) +
    geom_hline(yintercept=1,colour="#BA7517",linewidth=0.8,linetype="longdash") +
    geom_hline(yintercept=2,colour="#484f58",linewidth=0.5,linetype="dotted") +
    geom_line(linewidth=0.85,na.rm=TRUE) + geom_point(size=3,na.rm=TRUE) +
    annotate("text",x=-Inf,y=1.08,label="psi=1 (optimal)",
             hjust=-0.05,colour="#BA7517",size=2.8,family="mono") +
    scale_colour_manual(values=POL_COLORS,name="Policy") +
    scale_shape_manual(values=POL_SHAPES,name="Policy") +
    scale_linetype_manual(values=POL_LINES,name="Policy") +
    labs(x="N drones",y="psi = EWSAoI / LB",
         title="Optimality ratio psi",
         subtitle="psi=1 optimal · psi=2 SRP upper bound") +
    theme_kadota()
  dark_plotly(p)
})
```

### Slot allocation
```{r}
renderPlotly({
  d <- runs_r(); if(is.null(d)) return(no_data())
  d2 <- d %>% mutate(c2_pct=c2_share*100,
    policy=factor(policy,levels=names(POL_COLORS)),
    tip=sprintf("<b>%s</b><br>N=%d<br>C2=%.0f%%<br>Vid=%.0f%%",
                policy,N,c2_pct,100-c2_pct))
  p <- ggplot(d2,aes(x=factor(N),y=c2_pct,fill=policy,text=tip)) +
    geom_col(position="dodge",width=0.7) +
    geom_hline(yintercept=50,colour="#484f58",linewidth=0.5,linetype="dashed") +
    scale_fill_manual(values=POL_COLORS,name="Policy") +
    labs(x="N drones",y="C2 slot share (%)",
         title="C2 vs Video slot allocation",
         subtitle="50% = balanced · <50% = video-heavy · safety vs coherence") +
    theme_kadota()
  dark_plotly(p)
})
```

AoI Diagnosis {data-icon="fa-stethoscope"}
=====================================

Row {.tabset data-height=510}
-------------------------------------

### C2 Starvation — slots C2 por drone
```{r}
renderPlotly({
  d <- runs_r()
  if (is.null(d)||!"total_c2_ok"%in%names(d)) return(no_data())

  L_vid_val <- if("L_vid"%in%names(d)) round(mean(as.numeric(d$L_vid),na.rm=TRUE)) else "?"
  xv_name   <- input$xvar%||%"N"; if(!xv_name%in%names(d)) xv_name <- "N"
  xlab <- switch(xv_name,
    N="N drones", corridor_capacity="Capacity (simultaneous drones)",
    L_vid="L_vid", corridor_km="Corridor (km)", xv_name)

  d2 <- d %>%
    mutate(
      c2_per_drone = as.numeric(total_c2_ok) / pmax(as.numeric(N), 1),
      xv     = .data[[xv_name]],
      policy = factor(policy, levels=intersect(names(POL_COLORS), unique(policy))),
      tip    = sprintf("<b>%s</b><br>%s=%g<br>C2/drone=%.1f<br>h1=%.0f sl",
                       policy, xlab, xv, c2_per_drone, mean_h1))

  p <- ggplot(d2, aes(x=xv, y=c2_per_drone, colour=policy, shape=policy,
                      linetype=policy, text=tip)) +
    geom_line(linewidth=0.85, na.rm=TRUE) +
    geom_point(size=3, na.rm=TRUE) +
    scale_colour_manual(values=POL_COLORS, name="Policy") +
    scale_shape_manual(values=POL_SHAPES,  name="Policy") +
    scale_linetype_manual(values=POL_LINES,name="Policy") +
    labs(x=xlab, y="C2 slots received per drone",
         title="C2 scheduling rate — starvation diagnosis",
         subtitle=sprintf(
           "L_vid=%s → video AoI grows %sx faster than C2 → aoi-pure quase nunca agenda C2",
           L_vid_val, L_vid_val)) +
    theme_kadota()
  dark_plotly(p)
})
```

### EWSAoI = w·h1 + w·h2 — decomposição por política
```{r}
renderPlotly({
  d <- runs_r()
  if (is.null(d)) return(no_data())

  w_unc_v <- if("w_unc"%in%names(d)) mean(as.numeric(d$w_unc),na.rm=TRUE) else 0.33
  w_vid_v  <- if("w_vid"%in%names(d)) mean(as.numeric(d$w_vid),na.rm=TRUE) else 0.34

  d2 <- d %>%
    group_by(policy) %>%
    summarise(h1=mean(mean_h1,na.rm=TRUE), h2=mean(mean_h2,na.rm=TRUE), .groups="drop") %>%
    mutate(
      contrib_h1 = w_unc_v * h1,
      contrib_h2 = w_vid_v * h2,
      ewsaoi     = contrib_h1 + contrib_h2,
      policy     = fct_reorder(
                     factor(policy, levels=intersect(names(POL_COLORS), unique(policy))),
                     ewsaoi, .desc=TRUE))

  plot_ly(d2) %>%
    add_bars(x=~contrib_h1, y=~policy, orientation="h",
             name=sprintf("w_unc·h1  (C2,    w=%.4f)", w_unc_v),
             marker=list(color="#D85A30", line=list(color="#161b22",width=0.5)),
             hovertemplate="<b>%{y}</b><br>w·h1 = %{x:.1f} sl<extra>C2</extra>") %>%
    add_bars(x=~contrib_h2, y=~policy, orientation="h",
             name=sprintf("w_vid·h2  (video, w=%.4f)", w_vid_v),
             marker=list(color="#6BAED6", line=list(color="#161b22",width=0.5)),
             hovertemplate="<b>%{y}</b><br>w·h2 = %{x:.1f} sl<extra>Video</extra>") %>%
    layout(
      barmode="stack",
      title=list(
        text=sprintf("EWSAoI = w_unc·h1 + w_vid·h2   (w_unc=%.4f, w_vid=%.4f)",
                     w_unc_v, w_vid_v),
        font=list(color="#e6edf3", size=12)),
      xaxis=list(title="EWSAoI acumulado (slots)", gridcolor="#21262d", color="#8b949e"),
      yaxis=list(title="", color="#c9d1d9", tickfont=list(size=10)),
      paper_bgcolor="#161b22", plot_bgcolor="#0d1117",
      font=list(color="#c9d1d9", family="monospace"),
      legend=list(bgcolor="#161b22", bordercolor="#30363d", borderwidth=1,
                  orientation="h", x=0, y=-0.18),
      margin=list(l=140, r=20, t=50, b=70)) %>%
    config(displayModeBar=FALSE)
})
```

Drone Detail {data-icon="fa-table"}
=====================================

Row {data-height=60}
-------------------------------------

```{r}
uiOutput("ui_run_sel_row")
```

```{r, context="server"}
output$ui_run_sel_row <- renderUI({
  d <- dat()$drones; if(is.null(d)||!"run_id"%in%names(d)) return(NULL)
  runs_avail <- unique(d$run_id)
  div(style="display:flex;gap:12px;align-items:center;padding:8px 0",
    tags$label("Run:", style="font-size:12px;color:var(--color-text-secondary)"),
    selectInput("sel_run",NULL,
      choices=c("(all runs)"="__all__", runs_avail),
      selected=runs_avail[1],width="400px")
  )
})
```

Row {data-height=480}
-------------------------------------

### Per-drone metrics
```{r}
renderDT({
  d <- dat()$drones; if(is.null(d)||is.null(input$sel_run)) return(NULL)
  d2 <- d %>% filter(run_id==input$sel_run) %>%
    mutate(fdr_c2=round(slots_c2_ok/pmax(slots_c2_ok+slots_c2_fail,1),3),
           fdr_vid=round(slots_vid_ok/pmax(slots_vid_ok+slots_vid_fail,1),3),
           flight=exit_slot-entry_slot,
           h1_derived=round(flight/pmax(slots_c2_ok,1),2),
           h2_derived=round(flight/pmax(frames_delivered,1),2),
           h1_show=ifelse(mean_h1>0.01,round(mean_h1,2),h1_derived),
           h2_show=ifelse(mean_h2>0.01,round(mean_h2,2),h2_derived),
           across(where(is.double),~round(.x,2))) %>%
    select(drone_id,entry_slot,exit_slot,flight,
           slots_c2_ok,slots_vid_ok,fdr_c2,fdr_vid,
           frames_delivered,h1_show,h2_show,mean_r_vid,mean_r_tot)
  datatable(d2,
    colnames=c("UAV","Entry","Exit","Flight","C2 ok","Vid ok","FDR C2","FDR Vid",
               "Frames","h1","h2","R_vid","R_tot"),
    options=list(pageLength=20,dom="Bfrtip",scrollX=TRUE),
    style="bootstrap4",class="compact",filter="top") %>%
    formatStyle(1:13,backgroundColor="#0d1117",color="#c9d1d9") %>%
    formatStyle("h1_show",background=styleColorBar(c(0,200),"#1f4e79"),
                backgroundSize="98% 60%",backgroundRepeat="no-repeat",backgroundPosition="center") %>%
    formatStyle("fdr_c2",color=styleInterval(c(0.8,0.95),c("#f78166","#e3b341","#3fb950")))
})
```

AoI Time Series {data-icon="fa-wave-square"}
=====================================

Row {data-height=520}
-------------------------------------

### C2 AoI sawtooth
```{r}
renderPlotly({
  d <- dat()$series
  if (is.null(d)||nrow(d)==0) return(no_data("No series data"))
  is_agg <- isTRUE(dat()$is_agg)
  h1_col <- if("h1_slots"%in%names(d)) "h1_slots" else if("h1_mean"%in%names(d)) "h1_mean" else return(no_data("No h1 column"))
  d <- filter_run(d, input$sel_run)
  if (nrow(d)==0) return(no_data("No data for this run"))
  d <- d %>% mutate(slot_n=as.numeric(slot), h1_n=as.numeric(.data[[h1_col]]),
                    lbl=if(is_agg) paste0(policy," N=",N) else paste0("UAV",drone_id))
  if (!is_agg && "drone_id"%in%names(d)) d <- d %>% filter(as.integer(drone_id)<=8)
  plot_ly(d, x=~slot_n, y=~h1_n, color=~lbl, type="scatter", mode="lines",
          line=list(width=if(is_agg) 1.5 else 1),
          hovertemplate="slot %{x}<br>h1=%{y:.1f} sl<extra>%{fullData.name}</extra>") %>%
    layout(title=list(text=if(is_agg)"Mean C2 AoI over time (system)" else "AoI sawtooth evolution",
                      font=list(color="#e6edf3",size=12)),
           xaxis=list(title="Slot",gridcolor="#21262d",color="#8b949e"),
           yaxis=list(title="h1 (slots)",gridcolor="#21262d",color="#8b949e"),
           paper_bgcolor="#161b22",plot_bgcolor="#0d1117",
           font=list(color="#c9d1d9",family="monospace"),
           legend=list(bgcolor="#161b22",bordercolor="#30363d",borderwidth=1)) %>%
    config(displayModeBar=FALSE)
})
```

### SNR over time
```{r}
renderPlotly({
  d <- dat()$series
  if (is.null(d)||nrow(d)==0) return(no_data("No series data"))
  is_agg  <- isTRUE(dat()$is_agg)
  snr_col <- if("snr_db"%in%names(d)) "snr_db" else if("snr_mean"%in%names(d)) "snr_mean" else return(no_data("No SNR data"))
  d <- filter_run(d, input$sel_run)
  if (nrow(d)==0) return(no_data("No data for this run"))
  thresh <- 5
  d <- d %>% mutate(slot_n=as.numeric(slot), snr_n=as.numeric(.data[[snr_col]]),
                    lbl=if(is_agg) paste0(policy," N=",N) else paste0("UAV",drone_id))
  if (!is_agg) d <- d %>% filter(as.integer(drone_id)<=6)
  s_range <- range(d$slot_n, na.rm=TRUE)
  plot_ly(d, x=~slot_n, y=~snr_n, color=~lbl, type="scatter", mode="lines",
          line=list(width=1),
          hovertemplate="slot %{x}<br>SNR=%{y:.1f}dB<extra>%{fullData.name}</extra>") %>%
    add_lines(x=s_range, y=c(thresh,thresh), name="Threshold",
              line=list(color="#f78166",dash="dash",width=1), inherit=FALSE) %>%
    layout(title=list(text="SNR over time",font=list(color="#e6edf3",size=12)),
           xaxis=list(title="Slot",gridcolor="#21262d",color="#8b949e"),
           yaxis=list(title="SNR (dB)",gridcolor="#21262d",color="#8b949e"),
           paper_bgcolor="#161b22",plot_bgcolor="#0d1117",
           font=list(color="#c9d1d9",family="monospace"),
           legend=list(bgcolor="#161b22",bordercolor="#30363d",borderwidth=1)) %>%
    config(displayModeBar=FALSE)
})
```


Risk Analysis {data-icon="fa-shield-alt"}
=====================================

```{r risk_helpers, include=FALSE}
has_risk_summary <- reactive({
  d <- dat()$runs
  if (is.null(d)||nrow(d)==0||!"mean_r_tot"%in%names(d)) return(FALSE)
  any(suppressWarnings(as.numeric(d$mean_r_tot)) > 0.001, na.rm=TRUE)
})
has_risk_series <- reactive({
  d <- dat()$series
  if (is.null(d)||nrow(d)==0) return(FALSE)
  col <- if("r_tot_mean"%in%names(d)) "r_tot_mean" else if("r_tot"%in%names(d)) "r_tot" else return(FALSE)
  any(suppressWarnings(as.numeric(d[[col]])) > 0.001, na.rm=TRUE)
})

# Run selector for risk tab (separate from drone detail)
output$ui_risk_run <- renderUI({
  d <- dat()$drones
  if (is.null(d)||!"run_id"%in%names(d)) return(NULL)
  runs_avail <- sort(unique(d$run_id))
  div(style="display:flex;gap:12px;align-items:center;margin-bottom:10px",
    tags$label("Run:", style="font-size:12px;color:var(--color-text-secondary)"),
    selectInput("risk_run", NULL,
      choices = c("(all runs)"="__all__", runs_avail),
      selected = runs_avail[1], width="380px")
  )
})

# Risk-filtered series
risk_series <- reactive({
  d <- dat()$series
  if (is.null(d)||nrow(d)==0) return(NULL)
  if (!is.null(input$risk_run) && input$risk_run != "__all__" && "run_id"%in%names(d))
    d <- d %>% filter(run_id == input$risk_run)
  d
})
```

Row {data-height=60}
-------------------------------------

```{r}
uiOutput("ui_risk_run")
```

Row {data-height=420}
-------------------------------------

### R_sys vs N — all policies {data-width=500}

```{r}
renderPlotly({
  d <- runs_r()
  if (is.null(d)||!"mean_r_tot"%in%names(d)) return(no_data("No risk data"))
  d <- d %>% mutate(r=suppressWarnings(as.numeric(mean_r_tot))) %>%
    filter(!is.na(r), r>0)
  if (nrow(d)==0) return(no_data("mean_r_tot is zero — re-run aggregate_sim_data.R"))
  pols <- unique(d$policy)
  plt <- plot_ly()
  for (pol in pols) {
    dd <- d %>% filter(policy==pol) %>% arrange(N)
    plt <- plt %>% add_trace(data=dd, x=~N, y=~r, name=pol,
      type="scatter", mode="lines+markers",
      line=list(color=POL_COLORS[pol], width=2),
      marker=list(color=POL_COLORS[pol], size=8),
      hovertemplate=paste0("<b>",pol,"</b><br>N=%{x}<br>R_sys=%.3f<extra></extra>"))
  }
  plt %>% layout(
    title=list(text="System-wide risk vs N drones", font=list(color="#e6edf3",size=12)),
    xaxis=list(title="N drones", gridcolor="#21262d", color="#8b949e", dtick=1),
    yaxis=list(title="Mean R_sys", gridcolor="#21262d", color="#8b949e"),
    paper_bgcolor="#161b22", plot_bgcolor="#0d1117",
    font=list(color="#c9d1d9",family="monospace"),
    legend=list(bgcolor="#161b22",bordercolor="#30363d",borderwidth=1)) %>%
    config(displayModeBar=FALSE)
})
```

### Risk CDF (selected run) {data-width=500}

```{r}
renderPlotly({
  d_cdf <- dat()$cdf
  if (is.null(d_cdf)||nrow(d_cdf)==0) return(no_data("No CDF data — run aggregate_sim_data.R"))

  # Filter to selected run; if __all__ show one curve per policy (mean)
  sel <- input$risk_run
  if (!is.null(sel) && sel != "__all__") {
    d2 <- d_cdf %>% filter(run_id==sel) %>%
      mutate(r_num=as.numeric(r_tot), cdf_num=as.numeric(cdf), lbl=run_id)
  } else {
    # One curve per policy: average across runs of same policy
    d2 <- d_cdf %>%
      mutate(r_num=as.numeric(r_tot), cdf_num=as.numeric(cdf)) %>%
      group_by(policy, cdf_num=round(as.numeric(cdf),2)) %>%
      summarise(r_num=mean(r_num,na.rm=TRUE), .groups="drop") %>%
      mutate(lbl=policy)
  }
  if (nrow(d2)==0) return(no_data("No CDF points"))

  pols_in <- if(!is.null(sel)&&sel!="__all__") NULL else unique(d2$policy)
  plt <- plot_ly()
  for (g in unique(d2$lbl)) {
    dd <- d2 %>% filter(lbl==g) %>% arrange(r_num)
    col <- if(!is.null(pols_in)) POL_COLORS[g] else "#58a6ff"
    p95 <- quantile(dd$r_num, .95, na.rm=TRUE)
    plt <- plt %>%
      add_lines(data=dd, x=~r_num, y=~cdf_num, name=g,
        line=list(color=col, width=1.8),
        hovertemplate="R_sys=%{x:.2f}<br>CDF=%{y:.2f}<extra>%{fullData.name}</extra>")
  }
  # P95 line for selected run
  if (!is.null(sel) && sel != "__all__") {
    p95 <- quantile(d2$r_num, .95, na.rm=TRUE)
    plt <- plt %>%
      add_lines(x=c(p95,p95), y=c(0,1), name="P95",
        line=list(color="#f78166",dash="dash",width=1), inherit=FALSE)
  }
  plt %>% layout(
    title=list(text="Risk CDF", font=list(color="#e6edf3",size=12)),
    xaxis=list(title="R_sys value", gridcolor="#21262d", color="#8b949e"),
    yaxis=list(title="CDF", range=c(0,1), gridcolor="#21262d", color="#8b949e"),
    paper_bgcolor="#161b22", plot_bgcolor="#0d1117",
    font=list(color="#c9d1d9",family="monospace"),
    legend=list(bgcolor="#161b22",bordercolor="#30363d",borderwidth=1)) %>%
    config(displayModeBar=FALSE)
})
```

Row {data-height=460}
-------------------------------------

### Risk components over flight — per drone {data-width=750}

```{r}
renderPlotly({
  d <- risk_series()
  if (is.null(d)||nrow(d)==0) return(no_data("No series data — run aggregate_sim_data.R"))
  is_agg <- isTRUE(dat()$is_agg)

  # Column aliases
  rcols <- list(
    slot  = "slot",
    r_unc = if("r_unc_mean"%in%names(d)) "r_unc_mean" else if("r_unc"%in%names(d)) "r_unc" else NULL,
    r_vid = if("r_vid_mean"%in%names(d)) "r_vid_mean" else if("r_vid"%in%names(d)) "r_vid" else NULL,
    r_tot = if("r_tot_mean"%in%names(d)) "r_tot_mean" else if("r_tot"%in%names(d)) "r_tot" else NULL
  )
  if (is.null(rcols$r_tot)) return(no_data("No risk columns in series"))

  d <- d %>% mutate(
    slot_n  = as.numeric(slot),
    r_tot_n = as.numeric(.data[[rcols$r_tot]]),
    r_unc_n = if(!is.null(rcols$r_unc)) as.numeric(.data[[rcols$r_unc]]) else NA_real_,
    r_vid_n = if(!is.null(rcols$r_vid)) as.numeric(.data[[rcols$r_vid]]) else NA_real_
  ) %>% filter(!is.na(r_tot_n))

  if (is_agg) {
    # Agg mode: one subplot per policy × N combination
    groups <- d %>% distinct(policy, N) %>% arrange(policy, N)
    n_grps <- nrow(groups)
    if (n_grps == 0) return(no_data())
    n_cols <- min(4L, n_grps)
    n_rows <- ceiling(n_grps / n_cols)

    subplot_list <- lapply(seq_len(n_grps), function(gi) {
      g   <- groups[gi,]
      dd  <- d %>% filter(policy==g$policy, N==g$N) %>% arrange(slot_n)
      col <- POL_COLORS[g$policy]
      lbl <- paste0(g$policy, " N=", g$N)
      p <- plot_ly(dd, x=~slot_n) %>%
        add_lines(y=~r_tot_n, name="R_tot",
          line=list(color=col, width=1.5), showlegend=(gi==1),
          hovertemplate="slot %{x}<br>R_sys=%{y:.3f}<extra>R_tot</extra>")
      if (!all(is.na(dd$r_unc_n)))
        p <- p %>% add_lines(y=~r_unc_n, name="R_unc",
          line=list(color="#D85A30",dash="dot",width=1), showlegend=(gi==1),
          hovertemplate="slot %{x}<br>R_unc=%{y:.3f}<extra>R_unc</extra>")
      if (!all(is.na(dd$r_vid_n)))
        p <- p %>% add_lines(y=~r_vid_n, name="R_vid",
          line=list(color="#7F77DD",dash="dash",width=1), showlegend=(gi==1),
          hovertemplate="slot %{x}<br>R_vid=%{y:.3f}<extra>R_vid</extra>")
      p %>% layout(annotations=list(x=0.5, y=1.05, text=lbl, showarrow=FALSE,
                     xref="paper", yref="paper", font=list(color="#c9d1d9",size=9)))
    })
    subplot(subplot_list, nrows=n_rows, shareX=FALSE, shareY=FALSE,
            titleX=FALSE, titleY=FALSE) %>%
      layout(paper_bgcolor="#161b22", plot_bgcolor="#0d1117",
             font=list(color="#c9d1d9",family="monospace"),
             legend=list(bgcolor="#161b22",bordercolor="#30363d",borderwidth=1)) %>%
      config(displayModeBar=FALSE)
  } else {
    # Raw mode: one subplot per drone
    drones_avail <- sort(unique(d$drone_id))[1:min(6L,length(unique(d$drone_id)))]
    n_d <- length(drones_avail)
    n_cols <- min(3L, n_d); n_rows <- ceiling(n_d/n_cols)

    subplot_list <- lapply(seq_along(drones_avail), function(di) {
      uid <- drones_avail[di]
      dd  <- d %>% filter(drone_id==uid) %>% arrange(slot_n)
      lbl <- paste0("UAV ", uid)
      p <- plot_ly(dd, x=~slot_n) %>%
        add_lines(y=~r_tot_n, name="R_tot", showlegend=(di==1),
          line=list(color="#58a6ff",width=1.5),
          hovertemplate="slot %{x}<br>R_sys=%{y:.3f}<extra>R_tot</extra>")
      if (!all(is.na(dd$r_unc_n)))
        p <- p %>% add_lines(y=~r_unc_n, name="R_unc", showlegend=(di==1),
          line=list(color="#D85A30",dash="dot",width=1),
          hovertemplate="slot %{x}<br>R_unc=%{y:.3f}<extra>R_unc</extra>")
      if (!all(is.na(dd$r_vid_n)))
        p <- p %>% add_lines(y=~r_vid_n, name="R_vid", showlegend=(di==1),
          line=list(color="#7F77DD",dash="dash",width=1),
          hovertemplate="slot %{x}<br>R_vid=%{y:.3f}<extra>R_vid</extra>")
      p %>% layout(annotations=list(x=0.5, y=1.05, text=lbl, showarrow=FALSE,
                     xref="paper", yref="paper", font=list(color="#c9d1d9",size=9)))
    })
    subplot(subplot_list, nrows=n_rows, shareX=FALSE, shareY=TRUE,
            titleX=FALSE, titleY=FALSE) %>%
      layout(paper_bgcolor="#161b22", plot_bgcolor="#0d1117",
             font=list(color="#c9d1d9",family="monospace"),
             legend=list(bgcolor="#161b22",bordercolor="#30363d",borderwidth=1)) %>%
      config(displayModeBar=FALSE)
  }
})
```

### Pilot blindness {data-width=250}

```{r}
renderPlotly({
  d <- runs_r()
  if (is.null(d)||nrow(d)==0) return(no_data())
  # Pilot blindness: estimate from mean_h1
  # P(h1 > thresh) ~ 1 - thresh/mean_h1  (linear sawtooth approximation)
  thresh <- 10  # slots (667ms @ 15Hz)
  d2 <- d %>%
    mutate(blind_pct = pmax(0, (1 - thresh/pmax(mean_h1,0.1))) * 100,
           tip = sprintf("<b>%s</b><br>N=%d<br>Blind~%.1f%%<br>mean h1=%.1f sl",
                         policy, N, blind_pct, mean_h1))
  pols <- unique(d2$policy)
  plt <- plot_ly()
  for (pol in pols) {
    dd <- d2 %>% filter(policy==pol) %>% arrange(N)
    plt <- plt %>% add_trace(data=dd, x=~factor(N), y=~blind_pct, name=pol,
      type="bar", marker=list(color=POL_COLORS[pol]),
      text=~tip, hoverinfo="text")
  }
  plt %>% layout(
    barmode="group",
    title=list(text=paste0("Blind time\n(h1>",thresh,"sl)"), font=list(color="#e6edf3",size=11)),
    xaxis=list(title="N", gridcolor="#21262d", color="#8b949e"),
    yaxis=list(title="% slots", gridcolor="#21262d", color="#8b949e"),
    paper_bgcolor="#161b22", plot_bgcolor="#0d1117",
    font=list(color="#c9d1d9",family="monospace"),
    legend=list(bgcolor="#161b22",bordercolor="#30363d",borderwidth=1)) %>%
    config(displayModeBar=FALSE)
})
```


Video Transmission {data-icon="fa-video"}
=====================================

Row {data-height=90}
-------------------------------------

### Total Frames
```{r}
renderValueBox({
  d <- runs_r()
  n <- if(is.null(d)||!"total_frames"%in%names(d)) "--" else
       format(sum(as.integer(d$total_frames), na.rm=TRUE), big.mark=",")
  valueBox(n, "Frames delivered", icon="fa-film", color="primary")
})
```

### Mean h2
```{r}
renderValueBox({
  d <- runs_r()
  v <- if(is.null(d)||!"mean_h2"%in%names(d)) "--" else
       sprintf("%.1f sl", mean(d$mean_h2, na.rm=TRUE))
  valueBox(v, "Mean video AoI h2", icon="fa-clock", color="info")
})
```

### Video Channel Share
```{r}
renderValueBox({
  d <- runs_r()
  v <- if(is.null(d)||!"c2_share"%in%names(d)) "--" else
       sprintf("%.1f%%", mean((1 - d$c2_share)*100, na.rm=TRUE))
  valueBox(v, "Video slot share", icon="fa-signal", color="warning")
})
```

### Video FDR
```{r}
renderValueBox({
  d <- runs_r()
  v <- if(is.null(d)||!"total_vid_ok"%in%names(d)) "--" else {
    ok   <- sum(as.numeric(d$total_vid_ok),   na.rm=TRUE)
    fail <- sum(as.numeric(d$total_vid_fail), na.rm=TRUE)
    sprintf("%.3f", ok / max(ok + fail, 1))
  }
  valueBox(v, "Video FDR", icon="fa-check-circle", color="success")
})
```

Row {.tabset data-height=480}
-------------------------------------

### h2 vs N
```{r}
renderPlotly({
  d <- runs_r(); if(is.null(d)||!"mean_h2"%in%names(d)) return(no_data())
  has_K <- "K"%in%names(d) && length(unique(d$K))>1
  d2 <- d %>%
    mutate(policy=factor(policy,levels=intersect(names(POL_COLORS),unique(policy))),
           grp=if(has_K) paste0(policy," K=",K) else as.character(policy),
           tip=sprintf("<b>%s</b><br>N=%d%s<br>h2=%.1f sl",
                       policy, N, if(has_K) paste0(" K=",K) else "", mean_h2))
  p <- ggplot(d2, aes(x=N, y=mean_h2, colour=policy, shape=policy,
                       linetype=if(has_K) factor(K) else policy,
                       group=grp, text=tip)) +
    geom_line(linewidth=0.85, na.rm=TRUE) +
    geom_point(size=3, na.rm=TRUE) +
    scale_colour_manual(values=POL_COLORS, name="Policy") +
    scale_shape_manual(values=POL_SHAPES, name="Policy") +
    labs(x="Number of drones N", y="Video AoI h2 (slots)",
         title="Video AoI h2 vs N",
         subtitle=if(has_K)"Line style = K slots — use K filter for single view" else
                  "Video coherence cost vs fleet size") +
    theme_kadota()
  dark_plotly(p)
})
```

### h2 vs K
```{r}
renderPlotly({
  d <- runs_r()
  if(is.null(d)||!"K"%in%names(d)||!"mean_h2"%in%names(d)) return(no_data("No K dimension"))
  has_N <- length(unique(d$N))>1
  d2 <- d %>%
    mutate(policy=factor(policy,levels=intersect(names(POL_COLORS),unique(policy))),
           grp=if(has_N) paste0(policy," N=",N) else as.character(policy),
           tip=sprintf("<b>%s</b><br>K=%d%s<br>h2=%.1f sl",
                       policy, K, if(has_N) paste0(" N=",N) else "", mean_h2))
  p <- ggplot(d2, aes(x=K, y=mean_h2, colour=policy, shape=policy,
                       linetype=if(has_N) factor(N) else policy,
                       group=grp, text=tip)) +
    geom_line(linewidth=0.85, na.rm=TRUE) +
    geom_point(size=3, na.rm=TRUE) +
    scale_colour_manual(values=POL_COLORS, name="Policy") +
    scale_shape_manual(values=POL_SHAPES, name="Policy") +
    scale_x_continuous(breaks=c(1,2,4,8)) +
    labs(x="K simultaneous slots", y="Video AoI h2 (slots)",
         title="Video AoI h2 vs K",
         subtitle=if(has_N) "Use N filter to isolate — line style = N" else
                  "Effect of simultaneous slots on video coherence") +
    theme_kadota()
  dark_plotly(p)
})
```

### Frames per drone
```{r}
renderPlotly({
  d <- runs_r(); if(is.null(d)||!"frames_per_drone"%in%names(d)) return(no_data())
  has_K <- "K"%in%names(d) && length(unique(d$K))>1
  d2 <- d %>%
    mutate(policy=factor(policy,levels=intersect(names(POL_COLORS),unique(policy))),
           grp=if(has_K) paste0(policy," K=",K) else as.character(policy),
           tip=sprintf("<b>%s</b><br>N=%d%s<br>%.1f frames/drone",
                       policy, N, if(has_K) paste0(" K=",K) else "",
                       frames_per_drone))
  p <- ggplot(d2, aes(x=N, y=frames_per_drone, colour=policy, shape=policy,
                       linetype=if(has_K) factor(K) else policy,
                       group=grp, text=tip)) +
    geom_line(linewidth=0.85, na.rm=TRUE) +
    geom_point(size=3, na.rm=TRUE) +
    scale_colour_manual(values=POL_COLORS, name="Policy") +
    scale_shape_manual(values=POL_SHAPES, name="Policy") +
    labs(x="Number of drones N", y="Frames delivered per drone",
         title="Frame delivery vs N",
         subtitle="Higher = more video updates per UAV over the flight") +
    theme_kadota()
  dark_plotly(p)
})
```

### Video FDR vs N
```{r}
renderPlotly({
  d <- runs_r()
  if(is.null(d)||!"total_vid_ok"%in%names(d)) return(no_data())
  has_K <- "K"%in%names(d) && length(unique(d$K))>1
  d2 <- d %>%
    mutate(vid_fdr = as.numeric(total_vid_ok) /
                     pmax(as.numeric(total_vid_ok)+as.numeric(total_vid_fail), 1),
           policy=factor(policy,levels=intersect(names(POL_COLORS),unique(policy))),
           grp=if(has_K) paste0(policy," K=",K) else as.character(policy),
           tip=sprintf("<b>%s</b><br>N=%d%s<br>FDR vid=%.3f",
                       policy, N, if(has_K) paste0(" K=",K) else "", vid_fdr))
  p <- ggplot(d2, aes(x=N, y=vid_fdr, colour=policy, shape=policy,
                       linetype=if(has_K) factor(K) else policy,
                       group=grp, text=tip)) +
    geom_line(linewidth=0.85, na.rm=TRUE) +
    geom_point(size=3, na.rm=TRUE) +
    scale_colour_manual(values=POL_COLORS, name="Policy") +
    scale_shape_manual(values=POL_SHAPES, name="Policy") +
    scale_y_continuous(limits=c(0,1), labels=scales::percent) +
    labs(x="Number of drones N", y="Video frame delivery rate",
         title="Video FDR vs N",
         subtitle="Fraction of video slots that resulted in successful frame delivery") +
    theme_kadota()
  dark_plotly(p)
})
```

Load Analysis {data-icon="fa-tachometer-alt"}
=====================================

Row {data-height=460}
-------------------------------------

### Risk × Load {data-width=560}
```{r}
renderPlotly({
  d <- load_r(); if(is.null(d)||!"r_sys"%in%names(d)) return(no_data())
  d2 <- d %>% filter(!is.na(r_sys), r_sys > 0) %>%
    mutate(policy=factor(policy, levels=intersect(names(POL_COLORS), unique(policy))),
           tip=sprintf("<b>%s</b><br>rho=N/K=%.1f<br>R_sys=%.3e", policy, rho, r_sys))
  p <- ggplot(d2, aes(x=rho, y=r_sys, colour=policy, shape=policy,
                      linetype=policy, text=tip)) +
    geom_line(linewidth=0.85, na.rm=TRUE) +
    geom_point(size=3, na.rm=TRUE) +
    scale_colour_manual(values=POL_COLORS, name="Policy") +
    scale_shape_manual(values=POL_SHAPES,  name="Policy") +
    scale_linetype_manual(values=POL_LINES,name="Policy") +
    scale_x_log10() + scale_y_log10() +
    labs(x="Offered load  rho = N/K", y="Mean system risk R_sys",
         title="Risk × Offered Load",
         subtitle="Mean weighted composite risk — log/log scale") +
    theme_kadota()
  dark_plotly(p)
})
```

### AoI × Load {data-width=560}
```{r}
renderPlotly({
  d <- load_r(); if(is.null(d)) return(no_data())
  d2 <- d %>% filter(!is.na(ewsaoi)) %>%
    mutate(policy=factor(policy, levels=intersect(names(POL_COLORS), unique(policy))),
           tip=sprintf("<b>%s</b><br>rho=%.1f<br>EWSAoI=%.1f<br>LB=%.1f",
                       policy, rho, ewsaoi, lb_aoi))
  lb_line <- d2 %>% distinct(rho, lb_aoi) %>% arrange(rho) %>%
    mutate(policy=factor("lower_bound", levels=names(POL_COLORS)),
           ewsaoi=lb_aoi,
           tip=sprintf("<b>Lower Bound</b><br>rho=%.1f<br>LB=%.1f", rho, lb_aoi))
  d2 <- bind_rows(d2, lb_line)
  p <- ggplot(d2, aes(x=rho, y=ewsaoi, colour=policy, shape=policy,
                      linetype=policy, text=tip)) +
    geom_line(linewidth=0.85, na.rm=TRUE) +
    geom_point(size=3, na.rm=TRUE) +
    scale_colour_manual(values=POL_COLORS, name="Policy") +
    scale_shape_manual(values=POL_SHAPES,  name="Policy") +
    scale_linetype_manual(values=POL_LINES,name="Policy") +
    scale_x_log10() +
    labs(x="Offered load  rho = N/K", y="EWSAoI (slots)",
         title="AoI × Offered Load",
         subtitle="EWSAoI = w_unc·h1 + w_vid·h2  +  Kadota lower bound") +
    theme_kadota()
  dark_plotly(p)
})
```

Row {data-height=460}
-------------------------------------

### Video × Load {data-width=560}
```{r}
renderPlotly({
  d <- load_r(); if(is.null(d)) return(no_data())
  d2 <- bind_rows(
    d %>% mutate(metric="Frames/drone", val=frames_per_drone),
    d %>% mutate(metric="Video FDR",    val=vid_fdr)
  ) %>% filter(!is.na(val)) %>%
    mutate(policy=factor(policy, levels=intersect(names(POL_COLORS), unique(policy))),
           tip=sprintf("<b>%s</b><br>rho=%.1f<br>%s=%.3f", policy, rho, metric, val))
  p <- ggplot(d2, aes(x=rho, y=val, colour=policy, shape=policy,
                      linetype=policy, text=tip)) +
    geom_line(linewidth=0.85, na.rm=TRUE) +
    geom_point(size=3, na.rm=TRUE) +
    facet_wrap(~metric, scales="free_y") +
    scale_colour_manual(values=POL_COLORS, name="Policy") +
    scale_shape_manual(values=POL_SHAPES,  name="Policy") +
    scale_linetype_manual(values=POL_LINES,name="Policy") +
    scale_x_log10() +
    labs(x="Offered load  rho = N/K",
         title="Video × Offered Load",
         subtitle="Frames delivered per drone  ·  Video slot delivery rate") +
    theme_kadota()
  dark_plotly(p)
})
```

### C2 × Load {data-width=560}
```{r}
renderPlotly({
  d <- load_r(); if(is.null(d)) return(no_data())
  d2 <- bind_rows(
    d %>% mutate(metric="C2 throughput (pkt/slot)", val=tput_c2),
    d %>% mutate(metric="C2 FDR",                  val=fdr_c2)
  ) %>% filter(!is.na(val)) %>%
    mutate(policy=factor(policy, levels=intersect(names(POL_COLORS), unique(policy))),
           tip=sprintf("<b>%s</b><br>rho=%.1f<br>%s=%.4f", policy, rho, metric, val))
  p <- ggplot(d2, aes(x=rho, y=val, colour=policy, shape=policy,
                      linetype=policy, text=tip)) +
    geom_line(linewidth=0.85, na.rm=TRUE) +
    geom_point(size=3, na.rm=TRUE) +
    facet_wrap(~metric, scales="free_y") +
    scale_colour_manual(values=POL_COLORS, name="Policy") +
    scale_shape_manual(values=POL_SHAPES,  name="Policy") +
    scale_linetype_manual(values=POL_LINES,name="Policy") +
    scale_x_log10() +
    labs(x="Offered load  rho = N/K",
         title="C2 × Offered Load",
         subtitle="C2 throughput (packets/slot)  ·  C2 frame delivery rate") +
    theme_kadota()
  dark_plotly(p)
})
```

Slot Analysis {data-icon="fa-calendar-alt"}
=====================================

Row {data-height=60}
-------------------------------------

```{r}
uiOutput("ui_slot_run_row")
```

```{r, context="server"}
output$ui_slot_run_row <- renderUI({
  d <- dat()$drones
  if (is.null(d) || !"run_id" %in% names(d)) return(NULL)
  # Filter available runs to those matching current policy/N/K filters
  rf <- runs_r()
  runs_avail <- if (!is.null(rf) && "run_id" %in% names(rf)) {
    intersect(unique(d$run_id), unique(rf$run_id))
  } else unique(d$run_id)
  div(style="display:flex;gap:12px;align-items:center;padding:8px 0",
    tags$label("Run:", style="font-size:12px;color:var(--color-text-secondary)"),
    selectInput("sel_slot_run", NULL,
      choices  = c("(all runs)" = "__all__", sort(runs_avail)),
      selected = runs_avail[1], width = "420px"))
})

slot_drones_r <- reactive({
  d <- dat()$drones
  if (is.null(d) || nrow(d) == 0) return(NULL)
  sel <- input$sel_slot_run
  if (!is.null(sel) && sel != "__all__" && "run_id" %in% names(d))
    d <- d %>% filter(run_id == sel)
  d %>% mutate(
    flight_n      = pmax(as.numeric(exit_slot) - as.numeric(entry_slot), 1),
    c2_ok_n       = as.numeric(slots_c2_ok),
    c2_fail_n     = as.numeric(slots_c2_fail),
    vid_ok_n      = as.numeric(slots_vid_ok),
    vid_fail_n    = as.numeric(slots_vid_fail),
    unscheduled_n = pmax(flight_n - c2_ok_n - c2_fail_n - vid_ok_n - vid_fail_n, 0),
    c2_ok_pct     = c2_ok_n    / flight_n,
    c2_fail_pct   = c2_fail_n  / flight_n,
    vid_ok_pct    = vid_ok_n   / flight_n,
    vid_fail_pct  = vid_fail_n / flight_n,
    unsched_pct   = unscheduled_n / flight_n
  )
})
```

Row {data-height=105}
-------------------------------------

### C2 slots scheduled
```{r}
renderValueBox({
  d <- slot_drones_r()
  v <- if(is.null(d)) "--" else
       sprintf("%s (%.1f%%)", format(sum(d$c2_ok_n+d$c2_fail_n), big.mark=","),
               mean(d$c2_ok_pct+d$c2_fail_pct)*100)
  valueBox(v, "C2 slots scheduled", icon="fa-satellite-dish", color="primary")
})
```

### Video slots scheduled
```{r}
renderValueBox({
  d <- slot_drones_r()
  v <- if(is.null(d)) "--" else
       sprintf("%s (%.1f%%)", format(sum(d$vid_ok_n+d$vid_fail_n), big.mark=","),
               mean(d$vid_ok_pct+d$vid_fail_pct)*100)
  valueBox(v, "Video slots scheduled", icon="fa-video", color="info")
})
```

### Unscheduled slots
```{r}
renderValueBox({
  d <- slot_drones_r()
  v <- if(is.null(d)) "--" else
       sprintf("%.1f%%", mean(d$unsched_pct)*100)
  valueBox(v, "Unscheduled (mean/drone)", icon="fa-hourglass-half",
    color=if(!is.null(d)&&mean(d$unsched_pct)<0.3)"success" else "warning")
})
```

### Video loss rate
```{r}
renderValueBox({
  d <- slot_drones_r()
  v <- if(is.null(d)) "--" else {
    tot <- sum(d$vid_ok_n + d$vid_fail_n)
    sprintf("%.2f%%", sum(d$vid_fail_n) / max(tot,1) * 100)
  }
  valueBox(v, "Video slot loss rate", icon="fa-times-circle", color="danger")
})
```

Row {.tabset data-height=500}
-------------------------------------

### Per-drone breakdown
```{r}
renderPlotly({
  d <- slot_drones_r()
  if (is.null(d) || nrow(d) == 0) return(no_data())

  cats <- c("C2 ok","C2 fail","Video ok","Video fail","Unscheduled")
  cols <- c("C2 ok"="#3fb950","C2 fail"="#f78166",
            "Video ok"="#58a6ff","Video fail"="#e3b341","Unscheduled"="#484f58")

  lbl <- if("run_id" %in% names(d))
    paste0("UAV", d$drone_id, " [", d$run_id, "]") else paste0("UAV", d$drone_id)

  plt <- plot_ly()
  slot_cols <- list(
    list(name="C2 ok",      vals=d$c2_ok_n,    pct=d$c2_ok_pct),
    list(name="C2 fail",    vals=d$c2_fail_n,  pct=d$c2_fail_pct),
    list(name="Video ok",   vals=d$vid_ok_n,   pct=d$vid_ok_pct),
    list(name="Video fail", vals=d$vid_fail_n, pct=d$vid_fail_pct),
    list(name="Unscheduled",vals=d$unscheduled_n, pct=d$unsched_pct)
  )
  for (sc in slot_cols) {
    plt <- plt %>% add_trace(
      x=~sc$vals, y=~lbl, type="bar", orientation="h",
      name=sc$name, marker=list(color=cols[sc$name]),
      text=sprintf("%.1f%%", sc$pct*100),
      hovertemplate=paste0("<b>",sc$name,"</b><br>%{x} slots (%{text})<extra>%{y}</extra>"))
  }
  plt %>% layout(
    barmode="stack",
    title=list(text="Slot allocation per drone", font=list(color="#e6edf3",size=12)),
    xaxis=list(title="Slots", gridcolor="#21262d", color="#8b949e"),
    yaxis=list(title="", color="#c9d1d9", tickfont=list(size=9)),
    legend=list(bgcolor="#161b22",bordercolor="#30363d",borderwidth=1,
                traceorder="normal"),
    paper_bgcolor="#161b22", plot_bgcolor="#0d1117",
    font=list(color="#c9d1d9",family="monospace"),
    margin=list(l=160,r=20,t=40,b=40)) %>%
    config(displayModeBar=FALSE)
})
```

### Run summary
```{r}
renderPlotly({
  d <- slot_drones_r()
  if (is.null(d) || nrow(d) == 0) return(no_data())

  totals <- tibble(
    category = c("C2 ok","C2 fail","Video ok","Video fail","Unscheduled"),
    slots    = c(sum(d$c2_ok_n), sum(d$c2_fail_n),
                 sum(d$vid_ok_n), sum(d$vid_fail_n),
                 sum(d$unscheduled_n)),
    color    = c("#3fb950","#f78166","#58a6ff","#e3b341","#484f58")
  ) %>% filter(slots > 0)

  plot_ly(totals, labels=~category, values=~slots, type="pie",
    marker=list(colors=totals$color,
                line=list(color="#161b22", width=2)),
    textinfo="label+percent",
    hovertemplate="<b>%{label}</b><br>%{value} slots<br>%{percent}<extra></extra>") %>%
    layout(
      title=list(text="Total slot distribution", font=list(color="#e6edf3",size=12)),
      paper_bgcolor="#161b22",
      font=list(color="#c9d1d9",family="monospace"),
      legend=list(bgcolor="#161b22",bordercolor="#30363d",borderwidth=1),
      showlegend=TRUE) %>%
    config(displayModeBar=FALSE)
})
```

### Policy comparison
```{r}
renderPlotly({
  d <- dat()$drones
  rf <- runs_r()
  if (is.null(d) || is.null(rf)) return(no_data())

  # Keep only runs matching current filters
  d <- d %>% filter(run_id %in% unique(rf$run_id))
  if (nrow(d) == 0) return(no_data())

  d2 <- d %>%
    mutate(
      flight_n  = pmax(as.numeric(exit_slot) - as.numeric(entry_slot), 1),
      c2_ok_p   = as.numeric(slots_c2_ok)   / flight_n,
      c2_fail_p = as.numeric(slots_c2_fail) / flight_n,
      vid_ok_p  = as.numeric(slots_vid_ok)  / flight_n,
      vid_fail_p= as.numeric(slots_vid_fail)/ flight_n,
      unsched_p = pmax(1 - c2_ok_p - c2_fail_p - vid_ok_p - vid_fail_p, 0)
    ) %>%
    group_by(policy) %>%
    summarise(
      c2_ok    = mean(c2_ok_p,    na.rm=TRUE),
      c2_fail  = mean(c2_fail_p,  na.rm=TRUE),
      vid_ok   = mean(vid_ok_p,   na.rm=TRUE),
      vid_fail = mean(vid_fail_p, na.rm=TRUE),
      unsched  = mean(unsched_p,  na.rm=TRUE),
      .groups = "drop"
    )

  cats  <- c("C2 ok","C2 fail","Video ok","Video fail","Unscheduled")
  cols  <- c("#3fb950","#f78166","#58a6ff","#e3b341","#484f58")
  vals  <- list(d2$c2_ok, d2$c2_fail, d2$vid_ok, d2$vid_fail, d2$unsched)

  plt <- plot_ly()
  for (i in seq_along(cats)) {
    plt <- plt %>% add_trace(
      x = vals[[i]] * 100, y = d2$policy, type="bar", orientation="h",
      name=cats[i], marker=list(color=cols[i]),
      text=sprintf("%.1f%%", vals[[i]]*100),
      hovertemplate=paste0("<b>",cats[i],"</b><br>%{text}<extra>%{y}</extra>"))
  }
  plt %>% layout(
    barmode="stack",
    title=list(text="Mean slot allocation by policy", font=list(color="#e6edf3",size=12)),
    xaxis=list(title="% of flight slots", gridcolor="#21262d", color="#8b949e",
               ticksuffix="%", range=c(0,100)),
    yaxis=list(title="", color="#c9d1d9"),
    legend=list(bgcolor="#161b22",bordercolor="#30363d",borderwidth=1),
    paper_bgcolor="#161b22", plot_bgcolor="#0d1117",
    font=list(color="#c9d1d9",family="monospace"),
    margin=list(l=130,r=20,t=40,b=40)) %>%
    config(displayModeBar=FALSE)
})
```

Network Metrics {data-icon="fa-wifi"}
=====================================

Row {data-height=105}
-------------------------------------

### C2 Throughput
```{r}
renderValueBox({
  d <- net_r()
  v <- if(is.null(d)||!"tput_c2_pkt_s"%in%names(d)) "--" else
       sprintf("%.3f pkt/s", mean(d$tput_c2_pkt_s, na.rm=TRUE))
  valueBox(v, "Mean C2 throughput", icon="fa-satellite-dish", color="primary")
})
```

### Video Throughput
```{r}
renderValueBox({
  d <- net_r()
  v <- if(is.null(d)||!"tput_vid_fps"%in%names(d)) "--" else
       sprintf("%.3f fps", mean(d$tput_vid_fps, na.rm=TRUE))
  valueBox(v, "Mean video throughput", icon="fa-video", color="info")
})
```

### C2 FDR
```{r}
renderValueBox({
  d <- net_r()
  v <- if(is.null(d)||!"fdr_c2_n"%in%names(d)) "--" else
       sprintf("%.3f", mean(d$fdr_c2_n, na.rm=TRUE))
  valueBox(v, "C2 delivery rate", icon="fa-check-circle",
    color=if(!is.null(d)&&mean(d$fdr_c2_n,na.rm=TRUE)>0.9)"success" else "warning")
})
```

### Channel Utilization
```{r}
renderValueBox({
  d <- net_r()
  v <- if(is.null(d)||!"chan_util"%in%names(d)) "--" else
       sprintf("%.1f%%", mean(d$chan_util, na.rm=TRUE)*100)
  valueBox(v, "Channel utilization", icon="fa-broadcast-tower", color="warning")
})
```

Row {.tabset data-height=460}
-------------------------------------

### Throughput vs N
```{r}
renderPlotly({
  d <- net_r(); if(is.null(d)) return(no_data())
  has_K <- "K"%in%names(d) && length(unique(d$K))>1
  d2 <- bind_rows(
    d %>% mutate(metric="C2 (pkt/s)",  val=tput_c2_pkt_s,
                 grp=paste0(policy, if(has_K) paste0(" K=",K) else "")),
    d %>% mutate(metric="Video (fps)", val=tput_vid_fps,
                 grp=paste0(policy, if(has_K) paste0(" K=",K) else ""))
  ) %>% mutate(
    policy=factor(policy, levels=intersect(names(POL_COLORS), unique(policy))),
    tip=sprintf("<b>%s</b><br>N=%d<br>%s=%.4f", policy, N, metric, val))
  p <- ggplot(d2, aes(x=N, y=val, colour=policy, shape=policy, linetype=policy,
                      group=grp, text=tip)) +
    geom_line(linewidth=0.85, na.rm=TRUE) + geom_point(size=3, na.rm=TRUE) +
    facet_wrap(~metric, scales="free_y") +
    scale_colour_manual(values=POL_COLORS, name="Policy") +
    scale_shape_manual(values=POL_SHAPES, name="Policy") +
    scale_linetype_manual(values=POL_LINES, name="Policy") +
    labs(x="N drones", y="Throughput", title="Throughput vs N",
         subtitle="C2: packets/s per system · Video: frames/s per drone") +
    theme_kadota()
  dark_plotly(p)
})
```

### Delivery Rate vs N
```{r}
renderPlotly({
  d <- net_r(); if(is.null(d)) return(no_data())
  has_K <- "K"%in%names(d) && length(unique(d$K))>1
  d2 <- bind_rows(
    d %>% mutate(metric="C2 FDR",   val=fdr_c2_n,
                 grp=paste0(policy, if(has_K) paste0(" K=",K) else "")),
    d %>% mutate(metric="Video FDR", val=fdr_vid_n,
                 grp=paste0(policy, if(has_K) paste0(" K=",K) else ""))
  ) %>% mutate(
    policy=factor(policy, levels=intersect(names(POL_COLORS), unique(policy))),
    tip=sprintf("<b>%s</b><br>N=%d<br>%s=%.3f", policy, N, metric, val))
  p <- ggplot(d2, aes(x=N, y=val, colour=policy, shape=policy, linetype=policy,
                      group=grp, text=tip)) +
    geom_line(linewidth=0.85, na.rm=TRUE) + geom_point(size=3, na.rm=TRUE) +
    facet_wrap(~metric) +
    scale_colour_manual(values=POL_COLORS, name="Policy") +
    scale_shape_manual(values=POL_SHAPES, name="Policy") +
    scale_linetype_manual(values=POL_LINES, name="Policy") +
    scale_y_continuous(limits=c(0,1), labels=scales::percent) +
    labs(x="N drones", y="Delivery rate", title="Frame/Packet Delivery Rate vs N",
         subtitle="Higher = better — 1.0 means no losses") +
    theme_kadota()
  dark_plotly(p)
})
```

### Loss Rate vs N
```{r}
renderPlotly({
  d <- net_r(); if(is.null(d)) return(no_data())
  has_K <- "K"%in%names(d) && length(unique(d$K))>1
  d2 <- bind_rows(
    d %>% mutate(metric="C2 loss",   val=loss_c2,
                 grp=paste0(policy, if(has_K) paste0(" K=",K) else "")),
    d %>% mutate(metric="Video loss", val=loss_vid,
                 grp=paste0(policy, if(has_K) paste0(" K=",K) else ""))
  ) %>% mutate(
    policy=factor(policy, levels=intersect(names(POL_COLORS), unique(policy))),
    tip=sprintf("<b>%s</b><br>N=%d<br>%s=%.3f (%.1f%%)", policy, N, metric, val, val*100))
  p <- ggplot(d2, aes(x=N, y=val, colour=policy, shape=policy, linetype=policy,
                      group=grp, text=tip)) +
    geom_line(linewidth=0.85, na.rm=TRUE) + geom_point(size=3, na.rm=TRUE) +
    facet_wrap(~metric) +
    scale_colour_manual(values=POL_COLORS, name="Policy") +
    scale_shape_manual(values=POL_SHAPES, name="Policy") +
    scale_linetype_manual(values=POL_LINES, name="Policy") +
    scale_y_continuous(labels=scales::percent) +
    labs(x="N drones", y="Loss rate", title="Packet/Frame Loss Rate vs N",
         subtitle="Lower = better") +
    theme_kadota()
  dark_plotly(p)
})
```

### Latency vs N
```{r}
renderPlotly({
  d <- net_r(); if(is.null(d)) return(no_data())
  has_K <- "K"%in%names(d) && length(unique(d$K))>1
  d2 <- bind_rows(
    d %>% mutate(metric="C2 (s)",    val=lat_c2_s,
                 grp=paste0(policy, if(has_K) paste0(" K=",K) else "")),
    d %>% mutate(metric="Video (s)", val=lat_vid_s,
                 grp=paste0(policy, if(has_K) paste0(" K=",K) else ""))
  ) %>% mutate(
    policy=factor(policy, levels=intersect(names(POL_COLORS), unique(policy))),
    tip=sprintf("<b>%s</b><br>N=%d<br>%s=%.2f s", policy, N, metric, val))
  p <- ggplot(d2, aes(x=N, y=val, colour=policy, shape=policy, linetype=policy,
                      group=grp, text=tip)) +
    geom_line(linewidth=0.85, na.rm=TRUE) + geom_point(size=3, na.rm=TRUE) +
    facet_wrap(~metric, scales="free_y") +
    scale_colour_manual(values=POL_COLORS, name="Policy") +
    scale_shape_manual(values=POL_SHAPES, name="Policy") +
    scale_linetype_manual(values=POL_LINES, name="Policy") +
    labs(x="N drones", y="Delivery latency (s)", title="Delivery Latency vs N",
         subtitle="AoI-derived: h / update_rate — lower = fresher information") +
    theme_kadota()
  dark_plotly(p)
})
```

### Channel Utilization vs N
```{r}
renderPlotly({
  d <- net_r(); if(is.null(d)) return(no_data())
  has_K <- "K"%in%names(d) && length(unique(d$K))>1
  d2 <- d %>% mutate(
    policy=factor(policy, levels=intersect(names(POL_COLORS), unique(policy))),
    grp=paste0(policy, if(has_K) paste0(" K=",K) else ""),
    tip=sprintf("<b>%s</b><br>N=%d<br>util=%.1f%%", policy, N, chan_util*100))
  p <- ggplot(d2, aes(x=N, y=chan_util, colour=policy, shape=policy, linetype=policy,
                      group=grp, text=tip)) +
    geom_line(linewidth=0.85, na.rm=TRUE) + geom_point(size=3, na.rm=TRUE) +
    geom_hline(yintercept=1, colour="#BA7517", linewidth=0.7, linetype="longdash") +
    annotate("text", x=-Inf, y=1.02, label="100% capacity",
             hjust=-0.05, colour="#BA7517", size=2.8, family="mono") +
    scale_colour_manual(values=POL_COLORS, name="Policy") +
    scale_shape_manual(values=POL_SHAPES, name="Policy") +
    scale_linetype_manual(values=POL_LINES, name="Policy") +
    scale_y_continuous(labels=scales::percent, limits=c(0, NA)) +
    labs(x="N drones", y="Channel utilization", title="Channel Utilization vs N",
         subtitle="Scheduled slots / (sim_slots × K)") +
    theme_kadota()
  dark_plotly(p)
})
```

Manifest {data-icon="fa-list"}
=====================================

Row
-------------------------------------

### Run manifest — all scenario parameters
```{r}
renderDT({
  d <- dat()$manifest
  if(is.null(d)||nrow(d)==0) return(datatable(data.frame(msg="No manifest CSVs found"),options=list(dom="t")))
  datatable(d,options=list(pageLength=25,dom="Bfrtip",scrollX=TRUE),
    style="bootstrap4",class="compact",filter="top") %>%
    formatStyle(1:ncol(d),backgroundColor="#0d1117",color="#c9d1d9")
})
```
